GEE models

### 2017-10-15 doc/manuscript.Rmd
added details about manufactorers

At each examination, an 8-12 hour fasting blood sample was drawn from each
participant, followed by a 75g oral glucose tolerance test (OGTT) with a 30
minute and 2 hour blood draw. All blood samples were processed and frozen at
-70°C. Alanine aminotransferase (ALT) was measured using standard laboratory
procedures. Cholesterol, HDL, and triacylglycerides (TAG) were measured using Roche
Modular's enzymatic colorimetric tests (Mississauga, ON).  Both insulin
and glucose were derived from the OGTT at fasting, 30 minute, and 2 hour time
points. Specific insulin was measured using the Elecsys 1010 (Roche Diagnostics,
Basel, Switzerland) immunoassay analyser and electrochemiluminescence
immunoassay. This assay shows 0.05% cross-reactivity to intact human pro-insulin
and the Des 31,32 circulating split form (Linco Res. Inc), and has a coefficient of variation (CV) of 9.3%.
Glucose was determined using an enzymatic hexokinase (Roche Modular, Roche
Diagnostics) with a detection range of 0.11 (2 mg/dL) to 41.6 mmol/L.  The
inter-assay %CV is <1.1% and intra-assay %CV is < 1.9%.  All assays were
performed at the Banting and Best Diabetes Centre Core Lab at Mt Sinai Hospital.
Impaired fasting glucose (IFG), impaired glucose tolerance (IGT), and diabetes
were categorised using the 2006 WHO criteria [@WHO2006].

>>>>

At each examination, an 8-12 hour fasting blood sample was drawn from each
participant, followed by a 75g oral glucose tolerance test (OGTT) with a 30
minute and 2 hour blood draw. All blood samples were processed and frozen at
-70°C. Alanine aminotransferase (ALT) was measured using standard laboratory
procedures. Cholesterol, HDL, and triacylglycerides (TAG) were measured using Roche
Modular's enzymatic colorimetric tests (Roche Canada, Mississauga, Ontario, Canada).  Both insulin
and glucose were derived from the OGTT at fasting, 30 minute, and 2 hour time
points. Specific insulin was measured using the Elecsys 1010 (Roche Diagnostics,
Basel, Switzerland) immunoassay analyser and electrochemiluminescence
immunoassay. This assay shows 0.05% cross-reactivity to intact human pro-insulin
and the Des 31,32 circulating split form (Linco Res. Inc, St. Charles, Missouri, USA), and has a coefficient of variation (CV) of 9.3%.
Glucose was determined using an enzymatic hexokinase (Roche Modular, Roche
Diagnostics, Mississauga, Ontario, Canada) with a detection range of 0.11 (2 mg/dL) to 41.6 mmol/L.  The
inter-assay %CV is <1.1% and intra-assay %CV is < 1.9%.  All assays were
performed at the Banting and Best Diabetes Centre Core Lab at Mt Sinai Hospital.
Impaired fasting glucose (IFG), impaired glucose tolerance (IGT), and diabetes
were categorised using the 2006 WHO criteria [@WHO2006].
